% Robert Talbert CV
% Last updated on 26-06-2014

\documentclass[letterpaper]{article}

\usepackage{hyperref}
\usepackage{geometry}
\usepackage{enumitem}
\usepackage{amssymb, amsmath, amsfonts}
\usepackage[T1]{fontenc}
\usepackage[sc,osf]{mathpazo}

\def\name{Robert N. Talbert}

% Replace this with a link to your CV if you like, or set it empty
% (as in \def\footerlink{}) to remove the link in the footer:
\def\footerlink{}

% The following metadata will show up in the PDF properties
\hypersetup{
  colorlinks = true,
  urlcolor = black,
  pdfauthor = {\name},
  pdfkeywords = {mathematics, mathematics education, computer science},
  pdftitle = {\name: Curriculum Vitae},
  pdfsubject = {Curriculum Vitae},
  pdfpagemode = UseNone
}

\geometry{
  body={6.5in, 8.5in},
  left=1.0in,
  top=1.25in
}

% Customize page headers
\pagestyle{myheadings}
\markright{\name}
\thispagestyle{empty}

% Custom section fonts
\usepackage{sectsty}
\sectionfont{\rmfamily\mdseries\Large}
\subsectionfont{\rmfamily\mdseries\itshape\large}

\setlength\parindent{0em}

% Make lists without bullets
\renewenvironment{itemize}{
  \begin{list}{}{
    \setlength{\leftmargin}{1.5em}
	\setlength{\itemsep}{0in}
  }
}{
  \end{list}
}

\begin{document}

% Place name at left
{\Large \name}


\vspace{0.25in}

\begin{minipage}{0.45\linewidth}
  \href{http://www.gvsu.edu/}{Grand Valley State University} \\
  Department of Mathematics \\
  A-2-168 Mackinac Hall \\
  Allendale, MI 49401
\end{minipage}
\begin{minipage}{0.45\linewidth}
  \begin{tabular}{ll}
    Phone: & 616.331.8968 \\
    Email: & \href{mailto:talbertr@gvsu.edu}{\tt talbertr@gvsu.edu} \\
	Twitter: & \href{http://www.twitter.com/RobertTalbert}{@RobertTalbert} \\
    Homepage: & \href{http://faculty.gvsu.edu/talbertr/}{\tt http://faculty.gvsu.edu/talbertr/} \\
  \end{tabular}
\end{minipage}


\section*{Areas of Interest}

Cryptography, category theory, computer science; scholarship of teaching and learning including the inverted classroom, peer instruction, and use of technology to support active learning environments.

\section*{Education}

\begin{itemize}
  \item Ph.D. Mathematics, Vanderbilt University, 1997. Dissertation: \emph{Stratified and equivariant homology via homotopy colimits}, advised by Efstratios Prassidis. Areas of emphasis: Algebraic and geometric topology, category theory, ring theory, lattice theory, universal algebra.


  \item M.S. Mathematics, Vanderbilt University, 1994. Qualifying paper: \emph{The Leray-Serre spectral sequence, equivariance, and cohomology}. 

  \item B.S. Mathematics (\emph{magna cum laude in cursu honorum}), Tennessee Technological University, 1992. 

\end{itemize}


\section*{Employment}

\begin{itemize}
\item Associate Professor of Mathematics, Grand Valley State University 2011--present. 	
\item Assistant/Associate Professor of Mathematics and Computing Science, Franklin College 2001--2011. 
\item Assistant Professor of Mathematics, Bethel College (Indiana) 1997--2001. 
\item Master Teaching Fellow, Vanderbilt University Center for Teaching 1996--1997. 
\item Adjunct Faculty, Nashville State Community College 1995--1996. 
\item Graduate Teaching Scholar, Vanderbilt University 1993--1997. 
\end{itemize}


\section*{Teaching}

\subsection*{Courses taught or scheduled at GVSU}
MTH 201 (Calculus); MTH 202 (Calclulus 2); MTH 203 (Calculus 3); MTH 210 (Communicating in Mathematics); MTH 225 (Discrete Structures for Computer Science 1); MTH 227 (Linear Algebra 1); MTH 310 (Modern Algebra); MTH 312 (Cryptography and Privacy); MTH 325 (Discrete Structures for Computer Science 2); MTH 410 (Modern Algebra 2). 
 

\subsection*{Directed student projects at GVSU}
\begin{itemize}
	\item Elliptic curve cryptography (Christopher Grow, Winter 2012 for MTH 499).
	\item Fixed points and 2-cycles in columnar transposition ciphers (Beth Bjorkman, Summer 2012 for McNair Scholars Program and Fall 2012 for MTH 496). 
\end{itemize}


\subsection*{Courses taught prior to GVSU}

\begin{itemize}
	\item \textbf{Franklin College}: Quantitative Reasoning; Functions and Models; Calculus; Calculus II; Calculus III; Differential Equations; Linear Algebra; Methods of Problem Solving; Topics in Geometry; Modern Algebra; Special Topics (Cryptology); Computer Tools for Problem Solving; Operations Research; Cryptology, Privacy and Leadership; The Life and Works of C.S. Lewis.  
	\item \textbf{Bethel College}: College Algebra; Applied Calculus; Calculus I; Calculus II; Calculus III; Differential Equations; Modern Geometry; Abstract Algebra I; Abstract Algebra II; Topology; Christianity and the Life of the Mind. 
	\item \textbf{Vanderbilt University}: Calculus for Business and Life Science; Calculus I and II (liberal arts track); Calculus I and II (Science and Engineering track); Calculus III (Science and Engineering track). 
	\item \textbf{Nashville State Community College}: Algebra; Elementary Statistics; Business Mathematics. 
\end{itemize}


\subsection*{Directed student projects prior to GVSU}

Risk management and forecasting; Hyperbolic geometry and trigonometry; Elliptic curve cryptography; Computer investigations in geometry; Technology law; Geometry in art, architecture, and nature; Introduction to number theory; Mathematical methods in artificial intelligence; Taxicab geometry; Finite fields and applications; Computer modeling of hyperbolic geometry. 


\section*{Scholarship}

\subsection*{Research in progress}
\begin{itemize}
	\item Effects of flipped instruction on university remedial mathematics students with learning disabilities (with Amy Schelling). 
	\item Cognitive and metacognitive effects of flipped instruction in university Calculus (with Marcia Frobish). 
	\item Design of programming-centered discrete mathematics course for computer science students (with Hugh McGuire). 
	\item Book chapter in preparation: Talbert, R. (2014) Calculus. To appear in \emph{Flipping the College Classroom}, J. Waldrop and M. Bowdon, editors. 
	\item Article in preparation: Talbert, R. (2014) Technology as a tool for self-regulated learning in an inverted calculus course. In review at \emph{PRIMUS: Problems, Resources, and Issues in Undergraduate Mathematical Studies}. 
	\item Article in preparation: Talbert, R. (2013) Inverting the transition-to-proof course. In review at \emph{PRIMUS: Problems, Resources, and Issues in Undergraduate Mathematical Studies}. 
	\item Article in preparation: Bjorkman, B. and Talbert, R. (2013) Fixed points of columnar transposition ciphers. In review at \emph{Journal of Discrete Mathematical Sciences and Cryptography}.
\end{itemize}


\subsection*{Peer-reviewed articles}

\begin{itemize}
\item Talbert, R. (2014) The inverted classroom in introductory calculus: Best practices and potential benefits for the preparation of engineers. To appear in \emph{Proceedings of the American Society for Engineering Education 2014 Annual Conference}.  \textbf{Winner of Best Paper Award 2014, ASEE Mathematics Division.}
\item Talbert, R. (2013) Inverting the linear algebra classroom. Inverting the linear algebra classroom. \emph{PRIMUS: Problems, Resources, and Issues in Mathematics Undergraduate Studies}, 24:5, 361-374, \\ DOI: 10.1080/10511970.2014.883457
\item Talbert, R. (2013) Learning MATLAB in the inverted classroom. \emph{Computers in Education Journal}, \textbf{4}(2): 89--100.  
\item Talbert, R. (2006) The cycle structure and order of the rail fence cipher. \emph{Cryptologia}, \textbf{30}(2):159--172. 
\item Talbert, R. (1999) An isomorphism between Bredon and Quinn homology via homotopy colimits. \emph{Forum Mathematicum}, \textbf{11}:591--616. 
\end{itemize}

\subsection*{Other articles}
\begin{itemize}
	\item Talbert, R. (2012) The inverted classroom. \emph{Colleagues}, Vol. 9: Iss. 1, Article 7. \url{http:// scholarworks.gvsu.edu/colleagues/vol9/iss1/7/}.  
	\item Talbert, R. (2011) Using MATLAB to teach problem-solving techniques to first-year liberal arts students.\emph{ Mathworks News and Notes}, Fall issue.
	\item Gash, J. and Talbert, R. (2011) Integrating spreadsheets, visualization tools, and computational knowledge engines in a liberal arts calculus course. \emph{Proceedings of the Twenty-Second International Conference on Technology in Collegiate Mathematics}: \url{http://archives.math.utk.edu/ICTCM/i/22/C004.html}. 
	\item Talbert, R. (2011) Teaching MATLAB to a non-canonical audience. \emph{Proceedings of the Twenty-Second International Conference on Technology in Collegiate Mathematics}: \url{http://archives.math.utk.edu/ICTCM/i/22/C006.html}. 
	\item Talbert, R. (2009) A tale of two wikis: Upper-level mathematics meets Web 2.0.\emph{Proceedings of the Twentieth International Conference on Technology in Collegiate Mathematics}: \url{http://archives.math.utk.edu/ICTCM/i/20/C009.html}.
\end{itemize}

\subsection*{Book reviews}
\begin{itemize}
	\item \emph{Virtual Reality and Animation for MATLAB and Simulink Users: Visualization of Dynamic Models and Control Simulations} for INFORMS Journal on Computing: \url{http://www.informs.org/Pubs/IJOC/Book-Reviews/Volume-24-2012}. 
	\item \emph{Elliptic Curves: Number Theory and Cryptography} for MAA Reviews, \url{http://tinyurl.com/4cr5r3}, 22 August 2008.
	\item \emph{Finite Fields and Applications} for MAA Reviews, \url{http://tinyurl.com/4w5eqt}, 21 May 2008.
\end{itemize}

\subsection*{Online publication}

Author of \textbf{Casting Out Nines} blog (\url{http://chronicle.com/blognetwork/castingoutnines}), a sponsored online publication of the \emph{Chronicle of Higher Education} on mathematics, teaching, and technology.


\subsection*{Invited talks, workshops, and panel participation}
\begin{itemize}
	\item Workshop and keynote presentation to faculty at Lenoir-Rhyne University (title TBD), Hickory NC January 2015. 
	\item Three videos on the role of lecture and construction of screencasts for \emph{An Introduction to Evidence-Based Undergraduate STEM Teaching}, massively open online course offered through Coursera, October--December 2014. 
	\item ``(Re:)Designing Class for Flipped Learning Experiences''. Invited talk to faculty at California Polytechnic University, San Luis Obispo CA October 2014. 
	\item ``Formative pre-assessment in a flipped mathematics class using online tools''. Invited talk to faculty at Leeds University, Leeds, UK (online), September 2014. \url{http://roberttalbert.github.io/leeds}
	\item ``(Re:)Designing Class for Flipped Learning Experiences''. Webinar to faculty at Mount Aloysius College (PA), September 2014. \url{http://roberttalbert.github.io/mtaloysius}
	\item Workshop facilitator on the flipped classroom, GVSU Fall Teaching Conference, Grand Rapids, MI August 2014. 
	\item ``Flipping the university mathematics classroom: A gateway to lifelong learning.'' Invited keynote address at Workshop on Innovations in University Mathematics Teaching, Cardiff University, Cardiff, Wales UK July 2014. \url{http://roberttalbert.github.io/cardiffuniv}
	\item ``The conditions for invention: Using educational technology to make us more human''. Plenary address, Appalachian College Association Teaching and Learning Institute, Hickory, NC June 2014.
	\item ``(Re:)Designing class for flipped learning experiences''.  Workshop given at at Appalachian College Association Teaching and Learning Institute, Hickory, NC June 2014. 
	\item ``Four things I wish I had known about the flipped classroom''. Keynote address to faculty at Ecole Centrale Paris, Paris, France (online) June 2014. 
	\item Plenary speaker and instructor-in-residence, Appalachian College Association Teaching and Learning Institute, Hickory, NC June 2014. 
	\item Facilitator, Workshop on the inverted classroom. Delta College, University Center, MI February 2014. 
	\item Panelist, ``Assessment in Non-Traditional Classrooms''. Joint Meetings of the AMS/MAA, Baltimore, MD January 2014. 
	\item Facilitator, roundtable discussion on the flipped classroom, GVSU Faculty Teaching Roundtable, November 2013. 
	\item ``Deconstructing columnar transposition ciphers''. Mathematics Colloquium, Hope College, Holland, MI November 2013. 
	\item ``Deconstructing columnar transposition ciphers''. Mathematics Colloquium, Andrews University, Berrien Springs, MI October 2013.
	\item ``The inverted classroom and peer instruction: Designing classes for meaningful learning experiences.'' Keynote address, Michigan Mathematical Association of Two-Year Colleges, Auburn Hills, MI October 2013. 
	\item ``Giving your class an inverted classroom makeover''. Workshop for Michigan Mathematical Association of Two-Year Colleges, Auburn Hills, MI October 2013. 
	\item ``Flipping the college classroom: Transforming students into active learners''. Webinar for the Higher Ed Hero network, October 2013. 
	\item ``Better learning through voting''. Workshop at Ferris State University, Big Rapids, MI August 2013.
	\item ``Teaching and learning in the inverted classroom''. Workshop for faculty retreat at Lindsey Wilson College, Columbia, KY August 2013. 
	\item ``Teaching human beings''. Plenary address, Appalachian College Association Teaching and Learning Institute, Ferrum, VA June 2013. 
	\item ``Inverting the classroom to improve student learning and engagement''. Workshop given at at Appalachian College Association Teaching and Learning Institute, Ferrum, VA June 2013. 
	\item Participant in panel discussion on inquiry-based learning, Indiana MAA Section meeting, Indianapolis, IN October 2012. 
	\item ``Flip Your College Classroom: Increase Engagement and Experiential Learning''. Webinar given through Higher Ed Hero network, October 2012.
	\item ``Finding your next job''. Panel discussion presentation on Issues for Early Career Mathematicians, Mathematical Association of America MathFest, Madison, WI August 2012.
	\item ``Five questions about columnar transposition ciphers''. Guest presentation to Mathematics REU participants, Grand Valley State University, June 2012. 
	\item ``Flipping the Classroom: Overturning the Traditional Lecture''. Webinar given with Ike Shipley for The Blended Librarian, May 2012.
	\item ``Flipping the College Classroom.'' Webinar sponsored by Cengage Learning, March 2012.
	\item ``Flipping the College Classroom.'' Webinar given through American Mathematical Association of Two-Year Colleges, September 2011.
	\item  ``Inverting the Classroom, Improving Student Learning''. Presentation to graduate student teaching seminar, Mathematics Department, Indiana University Purdue University Indianapolis, Indianapolis, IN, March 2011. 
	\item ``Inquiry-Based MATLAB for General First-Year Students''. International Conference on Technology in Collegiate Mathematics, Denver, CO, March 2011. \url{http://bit.ly/g9ob42}
	\item ``Using Web-Based Presentation Tools to Promote Visual Thinking''. Workshop given at the Center for Research on Learning and Teaching, University of Michigan, Ann Arbor, MI, January 2011. \url{http://bit.ly/eI081T}
	\item ``Deconstructing Columnar Transposition Ciphers''. Department of Mathematical Sciences Faculty Colloquium; Ball State University, Muncie, IN, April 2009. \url{http://www.slideshare.net/rtalbert/deconstructing-columnar-transposition-ciphers}
	\item ``The Digital Signature Algorithm''. Guest lecture to MATH 390: Cryptography; Benedictine University, Lisle, IL, April 2008. 
	\item ``Protecting Ourselves with Mathematics: An Overview of Cryptology''. PBenedictine University Math Club; Benedictine University, Lisle, IL, April 2008.
\end{itemize}

\subsection*{Contributed talks}

\begin{itemize}
	\item ``The inverted classroom in introductory calculus: Best practices and potential benefits for the preparation of engineers.'' Mathematics Division paper session, American Society for Engineering Education annual conference, Indianapolis, IN June 2014. 
	\item ``Peer instruction in linear algebra''. Session on Innovative and Effective Ways to Teach Linear Algebra, Joint Meetings of AMS/MAA, Baltimore, MD January 2014. 
	\item ``A different kind of math: Addressing student difficulties with proof by flipping the transition-to-proof course''. Session on Flipping the Classroom, Joint Meetings of AMS/MAA, Baltimore, MD January 2014.
	\item ``Technology as a tool for self-regulated learning in an inverted calculus class''. Session on Teaching With Technology: Impact, Evaluation, and Reflection, Joint Meetings of AMS/MAA, Baltimore, MD January 2014.
	\item ``Inverting the transition-to-proof course''. Session on Research on the Teaching and Learning of Undergraduate Mathematics, Joint Meetings of AMS/MAA, Baltimore, MD January 2014.
	\item ``Clickers without the clickers: Using the web and students' personal devices for classroom response.'' GVSU Fall Teaching and Learning Conference, Grand Rapids, MI August 2013. 
	\item ``Making student learning visible in real time with peer instruction and web-based classroom response systems''. GVSU Scholarship of Teaching and Learning Academy, Grand Rapids, MI May 2013. 
	\item ``Transitioning to proofs in the inverted classroom''. Mathematical Association of America, Michigan Section meeting, Sault Ste. Marie, MI May 2013. 
	\item ``Using iPads to enhance the teaching and learning of mathematics''. GVSU Math in Action, Allendale, MI February 2013. 
	\item ``Learning MATLAB in the inverted classroom.'' American Society for Engineering Education Annual Conference, San Antonio, TX June 2012. 
	\item ``Classroom response systems in mathematics: Learning math better through voting''. GVSU Math in Action, Allendale, MI February 2012. 
	\item ``Making proofs click: Classroom response systems in transition-to-proof courses''. American Mathematical Society/Mathematical Association of America Joint Meetings, Boston, MA January 2012. 
	\item ``So you created a screencast. Now what?'' Techsmith, Inc. ScreencastCamp 2011, Okemos, MI August 2011. 
	\item ``Inquiry-based MATLAB for general first-year students''. International Conference on Technology in Collegiate Mathematics, Denver, CO March 2011. 
	\item ``Inverting the linear algebra classroom''. American Mathematical Society/Mathematical Association of America Joint Meetings, New Orleans, LA January 2011.
	\item ``A brief fly-through of cryptology for first-year students using active learning and common technology''.   American Mathematical Society/Mathematical Association of America Joint Meetings, New Orleans, LA January 2011.
	\item ``Teaching MATLAB to a Non-Canonical Audience''. International Conference on Technology in Collegiate Mathematics, Chicago, IL March 2010. 
	\item ``Integrating Spreadsheets, Visualization Tools, and Computational Knowledge Engines in a Liberal Arts Calculus Course'' (with J. Gash). International Conference on Technology in Collegiate Mathematics, Chicago, IL March 2010.
	\item ``A Tale of Two Wikis: Upper-Level Mathematics Courses meet Web 2.0''. International Conference on Technology in Collegiate Mathematics, San Antonio, TX March 2008.
\end{itemize}

\begin{center}
  \begin{footnotesize}
    List of contributed talks prior to 2008 available upon request
  \end{footnotesize}
\end{center}

\subsection*{Books}
\begin{itemize}
	\item Talbert, R. (2007) \emph{Test Bank} to accompany \emph{A Mathematical View of Our World}. Thomson Higher Education, Belmont, CA 2007.
\end{itemize}

\subsection*{Online course materials}
\begin{itemize}
	\item Screencasts for MTH 201: Calculus. \url{http://bit.ly/GVSUCalculus}. Created collaboratively in August-November 2013 with Prof. Marcia Frobish. 
	\item Screencasts for MTH 210: Communicating in Mathematics. \url{http://www.youtube.com/playlist?list=PL2419488168AE7001}. Created July-November 2012. 
\end{itemize}


\subsection*{Grants}
\begin{itemize}
	\item Michigan Association for Computer Users in Learning Grant, ``Technology for the Implementation of Peer Instruction and Interactive Engagement Pedagogies in Calculus and Discrete Structures'', June 2014, \$1200. 
	\item GVSU Center for Scholarly and Creative Excellence, Dissemination Grant, May 2014, \$750. 
	\item Co-Principal Investigator (with Scott Grissom, Shannon Biros, and Shaily Menon), National Science Foundation WIDER grant DUE-1256384, ``EAGER: GVSU Inventory of Instructional Practices'' September 2012, \$137,893.  
	\item GVSU Pew Technology Enhancement Grant 13-250, ``Implementing a Bring-Your-Own-Device Classroom Response System in Linear Algebra'' October 2012, \$2510. 
	\item GVSU Center for Scholarly and Creative Excellence, Faculty Scholarly Dissemination Grant-in-Aid, January 2012, \$500. 
\end{itemize}






\section*{Service}

\subsection*{Regional and national service activities}
\begin{itemize}
	\item Guest co-editor, Special Issue on Teaching with Technology, \emph{PRIMUS: Problems, Resources, and Issues in Mathematics Undergraduate Studies}, 2014.
	\item Chair, American Society for Engineering Education Mathematics Division 2013--2014. 
	\item Program Chair and Chair-elect, American Society for Engineering Education Mathematics Division, 2012--2013. 
	\item Director of Mathematical Association of America Project NExT, Michigan Section 2013--2014. 
	\item Editorial review board member of \emph{Mathematics Exchange} journal 2010--present. 
\end{itemize}


\subsection*{GVSU service activities}
\begin{itemize}
	\item Faculty Teaching and Learning Center Advisory Council, 2014--present. 
	\item University Academic Policy and Standards Committee, 2014--present. 
	\item Mathematics Department Student Affairs Committee, 2014--present. 
	\item Leader of Faculty Learning Community on the Inverted Classroom, 2013--2014. 
	\item Department Web Administrator, Mathematics Department 2012--2014.  
	\item Instructional Resources Coordinator, Mathematics Department 2011--present. 
	\item Social Media coordinator, Mathematics Department 2011--present.
	\item Seminar Coordinator, Mathematics Department 2011--2012; Co-Coordinator 2013--2014. 
	\item New faculty mentor, Mathematics Department, 2013--2014. 
	\item Election Committee (\emph{ad hoc} to coordinate special election to fill Assistant Chair position), Mathematics Department Winter 2013. 
	\item Mathematics Department Curriculum Committee, 2012--2013. 
\end{itemize}

\subsection*{Service activities prior to GVSU}
\begin{itemize}
	\item Director, Dual-Degree Program in Engineering, Franklin College 2006--2011. 
	\item Promotion and Tenure Committee, Franklin College 2006--2011 (Chair, 2008--2009). 
	\item Mentor, High School Dual-Enrollment Programs, Franklin College 2007--2010. 
	\item Curricular Assessment and Planning Committee, Franklin College 2002--2006 (Chair, 2003--2006). 
	\item Administrative Committee, Bethel College 1999--2001. 
	\item Strategic Planning Committee, Bethel College 1998--2001. 
	\item Director, Honors Program, Bethel College 1998--2001. 
	\item Financial Aid Committee, Bethel College 1997--1998. 
\end{itemize}


\section*{Professional Development}

\subsection*{Coursework}
\begin{itemize}
	\item The Data Scientist's Toolbox. Online course offered by Coursera, October--November 2014. 
	\item Programming Foundations with Python. Online course offered by Udacity; completion September 2014. 
	\item CS 215: Algorithms. Online course offered by Udacity; completion and certificate with highest distinction May 2014.  
	\item History and Future of (Mostly) Higher Education. Online course offered by Duke University through Coursera; completion and certificate with distinction January 2014. 
	\item Cryptography I. Online course offered by Stanford University through Coursera; completion with certificate August 2013. 
	\item Securing Digital Democracy. Online course offered by the University of Michigan through Coursera; completion with certificate December 2012.
	\item CS 101: Introduction to Computer Science. Online course offered by Udacity; completion with certificate April 2012. 
\end{itemize}


\subsection*{Workshops and minicourses}

\begin{itemize}
	\item The mathematics of paper folding. Mathematical Association of America MathFest, Madison, WI August 2012. 
	\item Discrete and computational geometry. American Mathematical Society/Mathematical Association of America Joint Meetings, Boston, MA January 2012. 
	\item Getting started in engineering education research. American Society for Engineering Education minicourse, Louisville, KY, June 2010. 
\end{itemize}

\subsection*{New course development}
\begin{itemize}
	\item \textbf{MTH 312: Cryptography and Privacy. }First offering at GVSU in Winter 2014 as part of Information, Innovation, and Technology theme in General Education curriculum. 
\end{itemize}


\section*{Professional Memberships}
\begin{itemize}
	\item Michigan Association for Computer Users in Learning, 2014--present. 
	\item International Association for Cryptologic Research 2006--2008 and 2013--present. 
	\item American Society for Engineering Education 2010--present.
	\item Association for Computing Machinery special interest group in Computer Science Education (ACM-SIGCSE), 2012--present.
	\item Mathematical Association of America 1997--present. 
	\item Mathematical Association of America, Michigan section 2011--present. 
\end{itemize}




\bigskip

% Footer
\begin{center}
  \begin{footnotesize}
    Last updated: \today \\
    %\href{\footerlink}{\texttt{\footerlink}}
  \end{footnotesize}
\end{center}

\end{document}